---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `cacc`: Conjunctive Analysis of Case Configurations

An R Package to compute Conjunctive Analysis of Case Configurations (CACC), Situational Clustering Tests, and Main Effects

## Description

This package contains a set of functions to conduct Conjunctive Analysis of Case Configurations (CACC) (Miethe, Hart & Regoeczi, 2008), to identify and quantify situational clustering in dominant case configurations (Hart, 2019), and to determine the main effects of specific variable values on the probabilities of outcome (Hart, Rennison & Miethe, 2017). Initially conceived as an exploratory technique for multivariate analysis of categorical data, CACC has developed to include formal statistical tests that can be applied in a wide variety of contexts. This technique allows examining composite profiles of different units of analysis in an alternative way to variable-oriented methods.

## Installation

You can install the development version of cacc from [GitHub](https://github.com/) with:

```{r install}
#| eval: false

# Check if the`devtools` package needs to be installed
if (!require("devtools")) install.package("devtools")

# Install the `cacc` package from GitHub
devtools::install_github("amoneva/cacc")
```

## Examples

```{r load}
library(cacc)
```

### CACC

```{r cacc}
# Calculate the CACC matrix
cacc_matrix <- test_data |> 
  cacc(
    ivs = c(iv1, iv2, iv3, iv4), 
    dv = dv1
  )

# Look at the first few rows
cacc_matrix |> head()
```

### Situational Clustering Tests

```{r chi}
# Compute a Chi-Square Goodness-of-Fit Test
cacc_matrix |> cluster_xsq()
```

```{r sci}
#| out.width: "50%"
#| out.heigth: "50%"

# Compute a Situational Clustering Index (SCI)
cacc_matrix |> cluster_sci()

# Plot a Lorenz Curve to visualize the SCI
cacc_matrix |> plot_sci()
```

### Main Effects

```{r effect}
#| out.width: "50%"
#| out.heigth: "50%"

# Compute the main effects for a specific variable value
cacc_matrix |> 
  main_effect(
    iv = iv4,
    value = 0,
    # Set to `FALSE` for a numeric vector of effects
    summary = TRUE
  )

# Plot the distribution of the main effect
cacc_matrix |> 
  plot_effect(
    iv = iv4,
    value = 0
  )
```

## References

-   Hart, T. C. (2019). Identifying Situational Clustering and Quantifying Its Magnitude in Dominant Case Configurations: New Methods for Conjunctive Analysis. *Crime & Delinquency, 66*(1), 143-159. https://doi.org/10.1177/0011128719866123
-   Hart, T. C., Rennison, C. M., & Miethe, T. D. (2017). Identifying Patterns of Situational Clustering and Contextual Variability in Criminological Data: An Overview of Conjunctive Analysis of  Case  Configurations. *Journal  of  Contemporary Criminal  Justice, 33*(2),  112–120. https://doi.org/10.1177/1043986216689746
-   Miethe, T. D., Hart, T. C., & Regoeczi, W. C. (2008). The Conjunctive Analysis of Case Configurations: An Exploratory Method for Discrete Multivariate Analyses of Crime Data. *Journal of Quantitative Criminology, 24*, 227–241. https://doi.org/10.1007/s10940-008-9044-8
